Appendix

### 2021-05-11 paper/preprint/preprint_version/paper_revised_submission_june2020_apa.Rmd
move june 2020 preprint files

```{r}
## Read in data 
load(here::here('data/data_preprint/all_vid_data_from_bbs_june2020.RData')) # all detections
load(here::here('data/data_preprint/all_centered_vid_data_from_bbs_june2020.RData')) # centered cropped
```

```{r}
load(here::here('data/data_preprint/gold_sample_from_bbs_june2020.RData')) # gold sample detections
load(here::here('data/data_preprint/gold_sample_annotations2020-01-31.RData')) # human annotations
```

@@

```{r examples, include = T, fig.env = "figure*", fig.pos = "h", fig.align='center', fig.width=8, fig.height=3.5, set.cap.width=T, num.cols.cap=2, fig.align = "center", fig.cap = "Example frames taken from the dataset, illustrating variability in the infant perspective across different locations. OpenPose detections are shown overlaid on these images (green dots = face, red dots = hands, orange dots = pose)."}
examples <- png::readPNG("figs/modifiedOPfigure_v4.png")
grid::grid.raster(examples)
```

@@

```{r}
## summary for all detections
summary_by_age <- all_vid_data %>%
  filter(!is.na(age_days)) %>%
  mutate(age_day_bin = cut(age_days, bins, labels=round(bin_starts/30,1))) %>%
  mutate(age_day_bin = as.numeric(as.character(age_day_bin))) %>%
  group_by(age_day_bin, child_id) %>%
  summarize(num_frames_total = sum(num_detect), num_faces = sum(num_faces), num_hands = sum(num_hands), prop_faces_summary = num_faces / num_frames_total, prop_hands_summary = num_hands / num_frames_total)
```

```{r}
## summary for centered detections
summary_by_age_center <- all_vid_data_center %>%
  filter(!is.na(age_days)) %>%
  mutate(age_day_bin = cut(age_days, bins, labels=round(bin_starts/30,1))) %>%
  mutate(age_day_bin = as.numeric(as.character(age_day_bin))) %>%
  group_by(age_day_bin, child_id) %>%
  summarize(num_frames_total = sum(num_frames), num_faces = sum(num_faces), num_hands = sum(num_hands), prop_faces_summary = num_faces / num_frames_total, prop_hands_summary = num_hands / num_frames_total)
```

```{R}
#### Make wide format for plotting
wide_uncropped <- summary_by_age %>%
  gather(region, prop, prop_faces_summary, prop_hands_summary) %>%
  mutate(approach = "uncropped",
         region = ifelse(region == "prop_faces_summary","Face","Hands"))  %>%
  filter(num_frames_total > 5000) # eliminate small data point that skews scaling

wide_center <- summary_by_age_center %>%
  gather(region, prop, prop_faces_summary, prop_hands_summary) %>%
  mutate(approach = "centered",
         region = ifelse(region == "prop_faces_summary","Face","Hands"))  %>%
  filter(num_frames_total > 5000) # eliminate small data point that skews scaling 
```

@@

ggplot(wide_uncropped, 
       aes(x=age_day_bin, y=prop, 
           size=log10(num_frames_total),
           col=region)) +
  geom_point(alpha=.2) +
  geom_smooth(span=10, aes(weight = num_frames_total), show.legend = FALSE) + # geom_smooth(show.legend = FALSE) or move these below legend?
  geom_smooth(data = wide_center, span=10, aes(weight = num_frames_total), show.legend = FALSE, 
              lty = 2, span=10, se = FALSE) +
  ylab('Proportion Detections') + 
  xlab('Age (Months)') +
  ylim(0,.5) +
  facet_grid(.~child_id) + 
  theme_few(base_size=9) +
  ggthemes::scale_color_solarized(name = "") + 
  scale_size_continuous(name = "Detections (Log 10)") +
  theme(legend.text=element_text(size=8)) +
  theme(legend.position="bottom")

@@

```{r}
vid_data_by_location <- all_vid_data %>%
  mutate(num_frames = num_detect) %>%
  mutate(age_day_bin = cut(age_days, bins, labels=round(bin_starts/30,1))) %>%
  mutate(age_day_bin = as.numeric(as.character(age_day_bin))) %>%
  left_join(meta) %>%
  filter(!is.na(Location)) %>%
  filter(count_locations==1)

vid_data_centered_by_location <- all_vid_data_center %>%
  mutate(age_day_bin = cut(age_days, bins, labels=round(bin_starts/30,1))) %>%
  mutate(age_day_bin = as.numeric(as.character(age_day_bin))) %>%
  left_join(meta) %>%
  filter(!is.na(Location)) %>%
  filter(count_locations==1)

# 
vid_data_by_location$Location = droplevels(vid_data_by_location$Location) 
vid_data_centered_by_location$Location = droplevels(vid_data_centered_by_location$Location) # get rid of unused levels (more than 1 location)

# merge locations that seem similar
levels_to_modify = levels(vid_data_by_location$Location)
levels_to_modify = levels(vid_data_centered_by_location$Location)
levels_to_modify[10] = 'Outside' # Outside on property
levels_to_modify[12] = 'Outside' # Off Property

# reset levels for both cropped/uncropped
levels(vid_data_centered_by_location$Location) <- levels_to_modify
levels(vid_data_by_location$Location) <- levels_to_modify

@@

```{r}
face_hand_by_location_centered<- vid_data_centered_by_location %>%
  group_by(Location,child_id,age_day_bin) %>%
  summarize(prop_faces = sum(num_faces)/sum(num_frames), prop_hands = sum(num_hands)/sum(num_frames), num_detect = sum(num_frames))  %>%
  group_by(Location) %>%
  filter(num_detect >12000)

face_hand_by_location <- vid_data_by_location %>%
  group_by(Location,child_id,age_day_bin) %>%
  summarize(prop_faces = sum(num_faces)/sum(num_frames), prop_hands = sum(num_hands)/sum(num_frames), num_detect = sum(num_frames))  %>%
  group_by(Location) %>%
  filter(num_detect >12000)

## Compute CIs for faces/hands by each location, and then merge back raw data so they can be plotted together
## Get rid of any locations where we didn't have enough data to make a CI (not more than 1 age_bin)
hands_to_plot_centered <- face_hand_by_location_centered %>%
  group_by(Location, child_id) %>%
  multi_boot_standard(col="prop_hands") %>%
  mutate(region = "Hands (Center)") %>%
  ungroup %>%
  left_join(face_hand_by_location_centered) %>%
  mutate(prop = prop_hands) %>%
  select(-prop_faces, -prop_hands) %>%
  filter(!is.na(ci_lower))

faces_to_plot_centered <- face_hand_by_location_centered %>%
  group_by(Location, child_id) %>%
  multi_boot_standard(col="prop_faces") %>%
  mutate(region = "Face (Center)") %>%
  ungroup %>%
  left_join(face_hand_by_location_centered) %>%
  mutate(prop = prop_faces) %>%
  select(-prop_faces, -prop_hands) %>%
  filter(!is.na(ci_lower))  # if we didn't have enough points to make a CI, filter

faces_to_plot_all <- face_hand_by_location %>%
  group_by(Location, child_id) %>%
  multi_boot_standard(col="prop_faces") %>%
  mutate(region = "Faces (All)") %>%
  ungroup %>%
  left_join(face_hand_by_location) %>%
  mutate(prop = prop_faces) %>%
  select(-prop_faces, -prop_hands) %>%
  filter(!is.na(ci_lower))  # if we didn't have enough points to make a CI, filter

hands_to_plot_all <- face_hand_by_location %>%
  group_by(Location, child_id) %>%
  multi_boot_standard(col="prop_hands") %>%
  mutate(region = "Hands (All)") %>%
  ungroup %>%
  left_join(face_hand_by_location) %>%
  mutate(prop = prop_hands) %>%
  select(-prop_faces, -prop_hands) %>%
  filter(!is.na(ci_lower))  # if we didn't have enough points to make a CI, filter

@@

ggplot(all_to_plot, aes(x = Location, y = mean, col=region)) + 
  geom_point(aes(x=Location, y=prop, size=log10(num_detect)), alpha=.1, position = position_dodge(width=.6)) +
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper, linetype=region),position = position_dodge(width=.6)) +
  coord_flip() + 
  ylab('Proportion Detected')+
  xlab('')+
  theme_few(base_size=8) +
  theme(legend.position = "bottom") +
  facet_grid(.~child_id)  +
  scale_size_continuous(name = "Detections (Log 10)") +
  scale_linetype_manual(values=c("solid", "dashed","solid","dashed"), name = "") +
  scale_color_manual(values = c("#268bd2", "#51acec", "#dc322f","#ea5e5c"), name = "") +
  theme(legend.text=element_text(size=8))

>>>>

```{r}
## Read in data 
# load(here::here('data/preprocessed_data/all_vid_data_from_bbs_july192020_merged.RData')) # all detections
# load(here::here('data/preprocessed_data/all_centered_vid_data_from_bbs_july2020.RData')) # centered cropped

load(here::here('data/data_preprint/all_vid_data_from_bbs_june2020.RData')) # all detections
load(here::here('data/data_preprint/all_centered_vid_data_from_bbs_june2020.RData')) # centered cropped

```{r}
load(here::here('data/preprocessed_data/gold_sample_from_bbs_july192020.RData')) # gold sample detections
load(here::here('data/data_preprint/gold_sample_annotations2020-01-31.RData')) # human annotations
```

@@

```{r examples, include = T, fig.env = "figure*", fig.pos = "h", fig.align='center', fig.width=8, fig.height=3.5, set.cap.width=T, num.cols.cap=2,  fig.fullwidth = TRUE, fig.align = "center", fig.cap = "Example frames taken from the dataset, illustrating variability in the infant perspective across different locations. OpenPose detections are shown overlaid on these images (green dots = face, red dots = hands, orange dots = pose)."}
examples <- png::readPNG("figs/modifiedOPfigure_v4.png")
grid::grid.raster(examples)
```

@@

```{r}
## summary for all detections
summary_by_age <- all_vid_data %>%
  ungroup() %>%
  filter(!is.na(age_days)) %>%
  mutate(age_day_bin = cut(age_days, bins, labels=round(bin_starts/30,1))) %>%
  mutate(age_day_bin = as.numeric(as.character(age_day_bin))) %>%
  group_by(age_day_bin, child_id) %>%
  summarize(num_frames_total = sum(num_detect), num_faces = sum(num_faces), num_hands = sum(num_hands), prop_faces_summary = num_faces / num_frames_total, prop_hands_summary = num_hands / num_frames_total)
```

```{r}
## summary for centered detections
# summary_by_age_center <- all_vid_data_center %>%
#   ungroup() %>%
#   filter(!is.na(age_days)) %>%
#   mutate(age_day_bin = cut(age_days, bins, labels=round(bin_starts/30,1))) %>%
#   mutate(age_day_bin = as.numeric(as.character(age_day_bin))) %>%
#   group_by(age_day_bin, child_id) %>%
#   summarize(num_frames_total = sum(num_frames), num_faces = sum(num_faces), num_hands = sum(num_hands), prop_faces_summary = num_faces / num_frames_total, prop_hands_summary = num_hands / num_frames_total)
```

```{r}
## get out summary by age for goldset hand-labelled frames
vid_info <- all_vid_data  %>%
  select(child_id, vid_name, age_days, age_day_bin)

summary_by_age_gold <- gold_sample %>%
  left_join(vid_info) %>%
  group_by(age_day_bin, child_id) %>%
  summarize(num_frames_total = n(), num_faces = sum(face_present_ketan), num_hands = sum(hand_present_ketan), prop_faces_summary = num_faces / num_frames_total, prop_hands_summary = num_hands / num_frames_total)

summary_by_age_adult_hands_gold <- gold_sample_no_child_hands %>%
  left_join(vid_info) %>%
  group_by(age_day_bin, child_id) %>%
  summarize(num_frames_total = n(), num_faces = sum(face_present_ketan), num_hands = sum(hand_present_ketan), prop_faces_summary = num_faces / num_frames_total, prop_hands_summary = num_hands / num_frames_total)

```{r}
# ## summary for centered detections
# summary_by_age_center <- all_vid_data_center %>%
#   filter(!is.na(age_days)) %>%
#   mutate(age_day_bin = cut(age_days, bins, labels=round(bin_starts/30,1))) %>%
#   mutate(age_day_bin = as.numeric(as.character(age_day_bin))) %>%
#   group_by(age_day_bin, child_id) %>%
#   summarize(num_frames_total = sum(num_frames), num_faces = sum(num_faces), num_hands = sum(num_hands), prop_faces_summary = num_faces / num_frames_total, prop_hands_summary = num_hands / num_frames_total)
```

```{R}
#### Make wide format for plotting
wide_uncropped <- summary_by_age %>%
  gather(region, prop, prop_faces_summary, prop_hands_summary) %>%
  mutate(approach = "uncropped",
         region = ifelse(region == "prop_faces_summary","Face","Hands"))  
  # filter(num_frames_total > 5000) # eliminate small data point that skews scaling

wide_gold <- summary_by_age_adult_hands_gold %>%
  gather(region, prop, prop_faces_summary, prop_hands_summary) %>%
  mutate(approach = "goldset",
         region = ifelse(region == "prop_faces_summary","Face","Hands"))

# wide_center <- summary_by_age_center %>%
#   gather(region, prop, prop_faces_center_summary, prop_hands_center_summary) %>%
#   mutate(approach = "centered",
#          region = ifelse(region == "prop_faces_center_summary","Face","Hands")) 
#   # filter(num_frames_total > 5000) # eliminate small data point that skews scaling 
```

@@

ggplot(wide_uncropped, 
       aes(x=age_day_bin, y=prop, 
           size=log10(num_frames_total),
           col=region)) +
  geom_point(alpha=.2) +
  geom_smooth(span=10, aes(weight = num_frames_total), show.legend = FALSE) + 
  geom_smooth(data = wide_gold, span=10, aes(weight = num_frames_total), show.legend = FALSE,
              lty = 2, span=10, se = FALSE) +
  ylab('Proportion Detections') + 
  xlab('Age (Months)') +
  ylim(0,.5) +
  facet_grid(.~child_id) + 
  theme_few(base_size=9) +
  ggthemes::scale_color_solarized(name = "") + 
  scale_size_continuous(name = "Detections (Log 10)") +
  theme(legend.text=element_text(size=8)) +
  theme(legend.position="bottom")

```{r}
## Appendix figure --- same trends in gold set
# ggplot(wide_gold, 
#        aes(x=age_day_bin, y=prop, 
#            size=log10(num_frames_total),
#            col=region)) +
#   geom_point(alpha=.2) +
#   geom_smooth(span=10, aes(weight = num_frames_total), show.legend = FALSE) + 
#   # geom_smooth(data = wide_gold, span=10, aes(weight = num_frames_total), show.legend = FALSE,
#               # lty = 2, span=10, se = FALSE) +
#   ylab('Proportion Detections') + 
#   xlab('Age (Months)') +
#   ylim(0,.5) +
#   facet_grid(.~child_id) +
#   theme_few(base_size=18) +
#   ggthemes::scale_color_solarized(name = "") + 
#   scale_size_continuous(name = "Detections (Log 10)") +
#   theme(legend.text=element_text(size=8)) +
#   theme(legend.position="bottom")

@@

```{r}
vid_data_by_location <- all_vid_data %>%
  mutate(age_day_bin = cut(age_days, bins, labels=round(bin_starts/30,1))) %>%
  mutate(age_day_bin = as.numeric(as.character(age_day_bin))) %>%
  left_join(meta) %>%
  filter(!is.na(Location)) %>%
  filter(count_locations==1)

# 
vid_data_by_location$Location = droplevels(vid_data_by_location$Location)

# merge locations that seem similar
levels_to_modify = levels(vid_data_by_location$Location)
levels_to_modify[10] = 'Outside' # Outside on property
levels_to_modify[12] = 'Outside' # Off Property

# reset levels for both cropped/uncropped
levels(vid_data_by_location$Location) <- levels_to_modify

@@

```{r}

face_hand_by_location <- vid_data_by_location %>%
  group_by(Location,child_id,age_day_bin) %>%
  summarize(num_detect = sum(num_frames),prop_faces = sum(num_faces)/num_detect, prop_hands = sum(num_hands)/num_detect,  prop_hands_center =  sum(num_hands_center)/num_detect, prop_faces_center = sum(num_faces_center)/num_detect)  %>%
  mutate(prop_faces_center = replace_na(prop_faces_center,0), prop_hands_center = replace_na(prop_hands_center,0)) %>%
  group_by(Location) %>%
  filter(num_detect >3000)

## Compute CIs for faces/hands by each location, and then merge back raw data so they can be plotted together
## Get rid of any locations where we didn't have enough data to make a CI (not more than 1 age_bin)
hands_to_plot_centered <- face_hand_by_location %>%
  group_by(Location, child_id) %>%
  multi_boot_standard(col="prop_hands_center") %>%
  mutate(region = "Hands (Center)") %>%
  ungroup %>%
  left_join(face_hand_by_location) %>%
  mutate(prop = prop_hands_center) %>%
  filter(!is.na(ci_lower))

faces_to_plot_centered <- face_hand_by_location %>%
  group_by(Location, child_id) %>%
  multi_boot_standard(col="prop_faces_center") %>%
  mutate(region = "Face (Center)") %>%
  ungroup %>%
  left_join(face_hand_by_location) %>%
  mutate(prop = prop_faces_center) %>%
  filter(!is.na(ci_lower))  # if we didn't have enough points to make a CI, filter

faces_to_plot_all <- face_hand_by_location %>%
  group_by(Location, child_id) %>%
  multi_boot_standard(col="prop_faces") %>%
  mutate(region = "Faces (All)") %>%
  ungroup %>%
  left_join(face_hand_by_location) %>%
  mutate(prop = prop_faces) %>%
  filter(!is.na(ci_lower))  # if we didn't have enough points to make a CI, filter

hands_to_plot_all <- face_hand_by_location %>%
  group_by(Location, child_id) %>%
  multi_boot_standard(col="prop_hands") %>%
  mutate(region = "Hands (All)") %>%
  ungroup %>%
  left_join(face_hand_by_location) %>%
  mutate(prop = prop_hands) %>%
  filter(!is.na(ci_lower))  # if we didn't have enough points to make a CI, filter

@@

ggplot(all_to_plot, aes(x = Location, y = mean, col=region)) + 
  geom_point(aes(x=Location, y=prop, size=log10(num_detect)), alpha=.1, position = position_dodge(width=.6)) +
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper, linetype=region),position = position_dodge(width=.6)) +
  coord_flip() + 
  ylab('Proportion Detected')+
  xlab('')+
  theme_few(base_size=18) +
  theme(legend.position = "bottom") +
  facet_grid(.~child_id)  +
  scale_size_continuous(name = "Detections (Log 10)") +
  scale_linetype_manual(values=c("solid", "dashed","solid","dashed"), name = "") +
  scale_color_manual(values = c("#268bd2", "#51acec", "#dc322f","#ea5e5c"), name = "") +
  theme(legend.text=element_text(size=8))
